Evaluating sensitivity to measurement error in dissolved gas measurements

### 2024-04-05 scripts/DG_sensitivity_to_measurement_error.Rmd
added simulation of saturation ratio uncertatinty

$$C = 1^{-6}B*C_{air}*exp(2700* \frac{1}{Tc} -  \frac{1}{298.15})$$
```{r c_sat}
C_sat <- C_a * B * 1e-6 * (H  * exp(2700*(1/(T_c + 273.15) - 1/298.15)))

@@

>>>>

$$C_{sat} = 1^{-6}B*C_{air}*(H^{\theta}*exp(2700* \frac{1}{Tc} -  \frac{1}{298.15}))$$
```{r c_sat}
C_sat <- C_a * B * 1e-6 * (H  * exp(2700*(1/(T_c + 273.15) - 1/298.15)))

@@

# Set up model for simulating true saturation ratio

The full equation for estimating the saturation ratio of $N_20$ gas dissolved in water is:

$$C_ratio = \frac{1^{-6}B \frac{V_{air}(Mr_h - Mr_r)}{(8.3144598 * K * V_{water}) + H^{\theta} \exp( 2700 * ( \frac{1}{K} - \frac{1}{298.15}) * Mr_h}}{1^{-6}B*C_{air}*exp(2700* \frac{1}{Tc} -  \frac{1}{298.15})}$$

``` {r}

C_ratio <- (1e-6 * B * ( V_g * ( C_e - C_a ) / ( 8.3144598 * ( T_c + 273.15 ) * V_w ) + H * exp( 2700 * ( 1 / ( T_c + 273.15 ) - 1 / 298.15 ) ) * C_e )) /
  (C_a * B * 1e-6 * (H  * exp(2700*(1/(T_c + 273.15) - 1/298.15))))

```
## Simulate measurement error for all observables
```{r simulate_me_ratio_all, message=F}
C_me_ratio <- rep( NA, 1e4 )

for( i in 1:length( C_me_ratio ) ){
C_me_ratio[ i ] <- (1e-6 * B_me[i] * ( V_g_me[i] * ( C_e_me[i] - C_a_me[i] ) / ( 8.3144598 * ( T_c_me[i] + 273.15 ) * V_w_me[i] ) + H * exp( 2700 * ( 1 / ( T_c_me[i] + 273.15 ) - 1 / 298.15 ) ) * C_e_me[i] )) /
  (C_a_me[i] * B_me[i] * 1e-6 * (H  * exp(2700*(1/(T_c_me[i] + 273.15) - 1/298.15)))) 
}

# combine into dataframe for ggplot. qplot, which accepts vectors,
# was deprecated in ggplot 3.4.0
C_ratio_df <- tibble(C_me_ratio = C_me_ratio)

ggplot(C_ratio_df, aes( x = C_me_ratio )) +  
  geom_histogram( binwidth = 0.01 ) + 
  geom_vline( xintercept = C_ratio , color = 'red' ) + 
  ggtitle( "Uncertainty in N2O saturation ratio due to cumulative \nmeasurment errors") +
  xlab( "saturation ratio")

ggplot(C_ratio_df, aes( x = C_me_ratio - C_ratio )) +  
  geom_histogram( binwidth = 0.001 ) + 
  geom_vline( xintercept = 0 , color = 'red' ) + 
  ggtitle( "Uncertainty in N2O saturation ratio due to cumulative \nmeasurment errors") +
  xlab( "absolute error (saturation ratio)")

# standard deviation of a saturation ratio value s:
sd(C_me_ratio) # 0.0.05479

# the 95% CI is therefore the computed value +/- 2 standard deviations
sd(C_me_ratio) * 1.96 # +/- 0.1073

# so any ratio within 0.1073 of 1.0 cannot be discerned as a source or sink?
```
